Hijacking Simulators with Universal Probabilistic Programming

### 2019-08-16 paper/learning/notes.tex

\section{ Questions for Tom}

>>>>

\section{Friday morning}
The subprograms within the simulator should be treated as nested probabilistic programs.

There are three ways we can do these things, rather than just an amortization

\subsection{Method 1: Learn the}
$\gamma_{a_{j}}(\cdot ; \eta_{a_{j}}, \cdot)$

As per we are currently planning. Relies on generating exact samples, which 
we have access due to the rejection sampling loops.

In this setting we can approximate the output
\subsection{Method 2: Proper amortized inference of sub-programs}

Learn a $q_{a_{j}}(z_{1:j}; \eta_{a_j}, \phi_j)$ and uses this as a proposal for the 
inner inference. 
I.e. if we learn that $q$ we could develop a more efficient rejection sampler by replacing the proposal.

I.e we are calibrating the proposal to make it more amenable to accepting samples. 
We can do this by using self normalized importance sampling on the inner program.

The likelihood is just a $\{0,1\}$ likelihood, ie Bernoulli.

\subsection{Method 3: Learn marginal likelihood $p(\cdot)$ approximation}

\begin{equation}
  p(x) = 
  \begin{cases}
  \prod^{n_x}_{j=1,{a_j}\in S_{R}} f_{a_j}(x_j ; \psi_j) \prod^{n_x}_{j=1,{a_j}\in S_{R}} \frac{P^{in}_{a_j}(x_j,\psi_j)}{P^{in}_{a_j}(\psi_j)} \\
  0
  \end{cases}
\end{equation}
The normalising constant inside (in) the rejection sampler is intractable.

The things inside of the rejection sampler are proportional to the following:
% \begin{equation}
%   \begin{cases}
%   \end{cases}
% \end{equation}

It is really important to ensure that these pairs of samples are unbiased.

If you minimise an $L_2$ norm the optimal 
\section{ Questions for Tom}
